Test of Adaptable User Interfaces

### 2015-07-07 paper.tex
Add Discussion to Approach

% =============================================================================
\section{Related Work}
% =============================================================================
Quality is very important in the software industry, and so are tests. They have been extensively studied by literature [TODO: some refs].
In a more modern context, Continuous Integration (CI) has been gaining popularity, hence is the need of automated tests.
An automated test is usually generated for the exact goal to achieve, then is executed and its results are compared to those expected, finally a report is constructed with a summary of the failures encountered. The report can be easily generated by IDE plugins as long as tests are well designed and use testing libraries (like JUnit). 
The increasing popularity of web-based softwares has obliged to develop tools to perform tests on these devices. Among them, are Selenium for browser-based applications, and Selendroid for Android applications.
Furthermore, GUIs have proven to be difficult to test, requiring new ways to verify them.
So automation of UI testing may be achieved by several means :
- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
- automated planning for hierarchical test case generation may be used which involves genetic algorithms [Ref: get https://en.wikipedia.org/wiki/Graphical_user_interface_testing#cite_note-Mem01-5]
- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]

@@

\subsection{Discussion and Analysis}
TODO

>>>>

% =============================================================================
\section{Related Work}
% =============================================================================
TODO

@@

\subsection{Discussion and Analysis}
Firstly, the number of lines to write for tests have been at least halved, as Table \ref{table:scriptssize} shows it.
\begin{table}
\begin{tabular}{l l r r r r}
			&					&	mobile	&	web0	&	web1	&	web2	\\
goal		&	plain Java	&	161		&	143		&	151		&	147		\\
			&	with Tobias	&	76		&	67		&	69		&	68		\\
filter		&	plain Java	&	/		&	350		&	402		&	369		\\
			&	with Tobias	&	/		&	88		&	93		&	92		\\
compare	&	plain Java	&	/		&	/		&	235		&	227		\\
			&	with Tobias	&	/		&	/		&	59		&	58
\end{tabular}
\caption{Comparison of number of lines for various functionalities and various versions for Tobias script and its generated test}
\label{table:scriptssize}
\end{table}
Secondly, the logical structure of the various tests for a same functionality and version is shared, and so the differences between these files are very localized : in the header of the file (preferences for the test) and in the implementations of the abstract groups (version details). So there is little variation from a shared abstract script for each file, as can be seen in Table \ref{table:scripts-similarity}.
\begin{table}
\begin{tabular}{l l r r r}
			&			&	shared	&	total	&	\%	\\
goal		&	mobile	&	48		&	76		&	63	\\
			&	web0	&	65		&	67		&	97	\\
			&	web2	&	65		&	68		&	95	\\
filter		&	web0	&	78		&	88		&	88	\\
			&	web2	&	89		&	92		&	96	\\
compare	&	web2	&	55		&	58		&	94
\end{tabular}
\caption{Comparison of number of shared lines between Tobias scripts and version web1 for a same functionality}
\label{table:scripts-similarity}
\end{table}
When small changes are applied to the UI, the scripts only differ by some lines. Even in the case of a change of platform (web to mobile) the scripts stay similar.
Lastly, there is also shared lines between files, whichever their version and functionality tested, because these tests proceed by steps, which can sometimes be the same for several scripts.
So this approach allows to reduce the amount of work, while it facilitates it by reducing differences between script versions.
